Cluster Difference Imaging Photometric Survey (CDIPS) II: A Jupiter-Sized Planet Candidate in IC~2602

### 2020-06-03 paper/ms.tex
update paper for multicolor

\subsubsection{Color Photometry}

HEB and, to a lesser extent, BEB scenarios, can be limited
by color photometry.

Ignoring color photometry,
the most plausible HEB scenarios for TOI 837 involve pairs of eclipsing M dwarfs.

\paragraph{Simple Example}
% SEE June 1, 2020 email in "Re: TOI-837.01" thread
As a simple example,
assume $M_2=M_3=0.2M_\odot$ in a twin HEB.
Assume PMS evolution, and convert between Mstar, delta mag, and Teff using MIST isochrones for a 50 Myr system. 
Take transmission functions (filters only; no instrument or atmosphere response) from the SVO filter profile service (CITE).
Integrate up blackbody functions over each bandpass for each star, and get estimates of the eclipse depths if there were a total eclipse (of either of the secondary or tertiary) with this set of parameters.
The apparent eclipse depths in each bandpass were:

BessellU: 5.03e-04
BessellB: 1.39e-03
BessellV: 3.31e-03
CousinsR: 5.59e-03
CousinsI: 9.69e-03
TESS: 9.18e-03

The relative depths are what are important (geometry lets them all be scaled to match the observed TESS depth of 40 ppt). The attached plot shows each bandpass, where the narrow ones are as in the order above, and the wide one is TESS.

U and B are ~10x shallower than TESS-band, because the M dwarf blackbody function turns over at ~2x longer wavelengths than the G dwarf blackbody (Wien's law).

@@

\paragraph{Complicated Implementation}
TODO, probably after U or B-band obtained.

\subsubsection{Summary}

@@

\acknowledgements
%
%This paper includes data collected by the TESS mission, which are
%publicly available from the Mikulski Archive for Space Telescopes
%(MAST).
%
%Funding for the TESS mission is provided by NASA's Science Mission
%directorate.
%
The authors thank...
%
We also thank the Heising-Simons Foundation for
their generous support of this work.
%
The Digitized Sky Survey was produced at the Space Telescope Science
Institute under U.S. Government grant NAG W-2166.
Figure~\ref{fig:scene} is based on photographic data obtained using
the Oschin Schmidt Telescope on Palomar Mountain.
%
This research made use of the Exoplanet Follow-up Observation
Program website, which is operated by the California Institute of
Technology, under contract with the National Aeronautics and Space
Administration under the Exoplanet Exploration Program.
%
% This research has made use of the SVO Filter Profile Service
% (\url{http://svo2.cab.inta-csic.es/theory/fps/}) supported from the Spanish
% MINECO through grant AYA2017-84089
%
% %
% Based on observations obtained at the Gemini Observatory, which is
% operated by the Association of Universities for Research in Astronomy,
% Inc., under a cooperative agreement with the NSF on behalf of the
% Gemini partnership: the National Science Foundation (United States),
% National Research Council (Canada), CONICYT (Chile), Ministerio de
% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
% and Korea Astronomy and Space Science Institute (Republic of Korea).
% %
% Observations in the paper made use of the High-Resolution Imaging
% instrument Zorro at Gemini-South. Zorro was funded by the NASA
% Exoplanet Exploration Program and built at the NASA Ames Research
% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
% Quigley.
% %
% This research has made use of the VizieR catalogue access tool, CDS,
% Strasbourg, France. The original description of the VizieR service was
% published in A\&AS 143, 23.
% %
% This work has made use of data from the European Space Agency (ESA)
% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
% for the DPAC has been provided by national institutions, in particular
% the institutions participating in the {\it Gaia} Multilateral
% Agreement.
%
% (Some of) The data presented herein were obtained at the W. M. Keck
% Observatory, which is operated as a scientific partnership among the
% California Institute of Technology, the University of California and
% the National Aeronautics and Space Administration. The Observatory was
% made possible by the generous financial support of the W. M. Keck
% Foundation.
% The authors wish to recognize and acknowledge the very significant
% cultural role and reverence that the summit of Maunakea has always had
% within the indigenous Hawaiian community.  We are most fortunate to
% have the opportunity to conduct observations from this mountain.
%
% \newline
%

>>>>

\newpage
\subsubsection{Color Photometry}

HEB and to a lesser extent BEB scenarios can be limited
by color photometry.
In the absense of color photometry, the most plausible HEB scenarios for TOI
837 involve pairs of eclipsing M dwarfs (Figure~\ref{fig:fpscenario}).
These eclipses are redder than eclipses of the G-dwarf \tn.
Observations that the transit depth does not decrease
going to blue bands therefore limits the plausibility of these scenarios.

\paragraph{Simple Example}
% SEE June 1, 2020 email in "Re: TOI-837.01" thread
As a simple example, assume $M_2=M_3=0.2M_\odot$ in a twin HEB.
Assume PMS evolution, and
use MIST isochrones for a 35 Myr system to convert between stellar properties. 
Take transmission functions (filters only; no instrument or atmosphere
response) from the SVO filter profile service\footnote{\url{http://svo2.cab.inta-csic.es/theory/fps/}}.
Integrate up blackbody functions over each bandpass for each star, and
get estimates of the eclipse depths if there were a total eclipse (of
either of the secondary or tertiary) with this set of parameters.  The
apparent eclipse depths in various Bessel and Cousins bandpasses are:
\begin{align}
%FIXME: check these numbers
  \delta_{\rm U_B} &= 5.03\times10^{-4} \ ({\rm Bessel\ U})\nonumber \\
  \delta_{\rm B_B} &= 1.39\times10^{-3}\ ({\rm Bessel\ B})\nonumber \\
  \delta_{\rm V_B} &= 3.31\times10^{-3}\ ({\rm Bessel\ V})\nonumber \\
  \delta_{\rm R_C} &= 5.59\times10^{-3}\ ({\rm Cousins\ R})\nonumber \\
  \delta_{\rm I_C} &= 9.69\times10^{-3}\ ({\rm Cousins\ I})\nonumber \\
  \delta_{\rm T}   &= 9.18\times10^{-3}\ ({\rm TESS})
\end{align}

Our chief interest is the relative depths, because geometry lets all the
depths be scaled to match the observed TESS depth of $\approx$43 ppt.
(In this case, all depths would be scaled down by a multiplicative factor of
2.1).

The crucial point is that the bluest bands--- U and B---are roughly 10
times shallower than TESS-band, because the M dwarf blackbody function
turns over at 2 times longer wavelengths than the G dwarf blackbody
(Wien's law).

@@

\paragraph{Limits on Masses of Bound Companions}

With this intuition in place, we derived the limits on masses of bound
hierarchical eclipsing companions as follows.  We assumed that each
system was composed of the primary (\tn), plus a tertiary companion
eclipsing a secondary companion every 8.3 days.

For secondary masses ranging from 0.07 to 1.10 $M_\odot$, and
mass ratios ($M_3/M_2$) from 0.1 to 1, we then 
calculated the observed maximal eclipse depth of Star 3 in front of
Star 2 in a number of bandpasses.
As before, we interpolated between mass, effective temperature, and radius
assuming the MIST isochrones for a 35$\,$Myr old system,
and also assumed that each source had a blackbody spectrum.

We excluded systems for which the maximal eclipse depth in TESS-band
was less than the observed depth ({\it i.e.}, systems for which the tertiary
was too small).
For the systems with maximal eclipse depths in TESS-band greater than
the observed TESS-band depth, we then calculated the multiplicative
factor required to shrink the depth (from the $b=0$ case) to match the
observed eclipse depth in the TESS-band.
We then scaled the depths in each of the other bandpasses by this
fixed geometric factor.

We then asked: given a fixed secondary mass, are there any tertiary
companions for which the expected $\delta_{\rm R_C}$ is larger than
the observed Rc-band depth?
In cases for which the answer was yes, we could not rule out such
hierarchical eclipsing binary systems.
Conversely, we were able to rule out systems
for which at fixed secondary mass no tertiary mass would
enable eclipses (in ${\rm R_C}$-band) of the necessary depth.

For a lower limit on $\delta_{\rm R_C}$ of 32 parts per thousand,
we found that the transition between systems that would produce
eclipses that no matter what were ``too red'', and systems that would
produce eclipses that could be sufficiently blue happens in \tn\ (for
${\rm R_C}$-band) at 0.54$M_\odot$.
The corresponding limit is shown in Figure~\ref{fig:fpscenario}.

{\bf If we could obtain a similar limit in B-band, it would 
	solidify this result (because it would drive the HEB system to be even bluer).}

\paragraph{Limits on Masses of Projected Companions}

Ignoring the effects of interstellar reddening,
the constraint that $M_2 \gtrsim 0.54 M_\odot$ based on
colors applies to background eclipsing binaries as well.
However, the blue eclipses produced by such systems ({\it e.g.}, a background G2V+K6V binary)
can be kept while making the systems fainter by moving them to greater
distances.
The only way to definitively rule out such scenarios is to 
prove that the loss of light is from the target star,
for instance by detecting the Rossiter-McLaughlin effect
during a transit.

Such scenarios are somewhat contrived in that since 
no secondary eclipse is observed, they require either
eccentric orbits to avoid secondary eclipses, or else a
background twin binary system at double
the orbital period.

\newpage
\subsubsection{Summary}

@@

\acknowledgements
%
%This paper includes data collected by the TESS mission, which are
%publicly available from the Mikulski Archive for Space Telescopes
%(MAST).
%
%Funding for the TESS mission is provided by NASA's Science Mission
%directorate.
%
The authors thank...
%
We also thank the Heising-Simons Foundation for
their generous support of this work.
%
The Digitized Sky Survey was produced at the Space Telescope Science
Institute under U.S. Government grant NAG W-2166.
Figure~\ref{fig:scene} is based on photographic data obtained using
the Oschin Schmidt Telescope on Palomar Mountain.
%
This research made use of the Exoplanet Follow-up Observation
Program website, which is operated by the California Institute of
Technology, under contract with the National Aeronautics and Space
Administration under the Exoplanet Exploration Program.
%
This research has made use of the SVO Filter Profile Service
(\url{http://svo2.cab.inta-csic.es/theory/fps/}) supported from the Spanish
MINECO through grant AYA2017-84089
%
% %
% Based on observations obtained at the Gemini Observatory, which is
% operated by the Association of Universities for Research in Astronomy,
% Inc., under a cooperative agreement with the NSF on behalf of the
% Gemini partnership: the National Science Foundation (United States),
% National Research Council (Canada), CONICYT (Chile), Ministerio de
% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
% and Korea Astronomy and Space Science Institute (Republic of Korea).
% %
% Observations in the paper made use of the High-Resolution Imaging
% instrument Zorro at Gemini-South. Zorro was funded by the NASA
% Exoplanet Exploration Program and built at the NASA Ames Research
% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
% Quigley.
% %
% This research has made use of the VizieR catalogue access tool, CDS,
% Strasbourg, France. The original description of the VizieR service was
% published in A\&AS 143, 23.
% %
% This work has made use of data from the European Space Agency (ESA)
% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
% for the DPAC has been provided by national institutions, in particular
% the institutions participating in the {\it Gaia} Multilateral
% Agreement.
%
% (Some of) The data presented herein were obtained at the W. M. Keck
% Observatory, which is operated as a scientific partnership among the
% California Institute of Technology, the University of California and
% the National Aeronautics and Space Administration. The Observatory was
% made possible by the generous financial support of the W. M. Keck
% Foundation.
% The authors wish to recognize and acknowledge the very significant
% cultural role and reverence that the summit of Maunakea has always had
% within the indigenous Hawaiian community.  We are most fortunate to
% have the opportunity to conduct observations from this mountain.
%
% \newline
%
